\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Edit section 7 (quantitative study) for style

\section{Quantitative Testing}
\label{sec:quantitative}
We performed our quantitative experiments at a behavioral laboratory on many participants at a time, using instrumentation to capture evaluation metrics. We confirmed prior stumbling points and user behaviors and validated our proposed design improvements.

@@

\subsection{Procedure}
We ran our experiment at Xlab~\cite{xlab}, an experimental social science laboratory. Xlab had 36 workstations with identical Windows~7 laptops, with workstation partitions to discourage participants from looking at other screens. At the beginning of each session, we used a script to revert the computers to a clean image; download Firefox, Chrome, Internet Explorer, VLC media player, and Tor Browser 5.0.3 (instrumented versions that logged user interactions, with/without our proposed UI changes); set up one of the three simulated environments (E1, E2, or E3); and start recording the computer screen. We manually assigned interface--environment combinations to each computer.

We received informed consent after talking about the study (Appendix~\ref{quantitative-script}). We instructed participants to use Tor to complete their worksheet (Appendix~\ref{summative-worksheet}) and gave them 40 minutes to complete the task. Researchers maintained minimal interactions with the participants. After the experiment and exit survey (Appendix~\ref{quantitative-exit-survey}), we gave each participant \$30 for their time.

\subsection{Results} 
In this section, we use OLD to refer to the original interface (Figure~\ref{fig:old-interface}) and NEW to refer the version with our changes (Figure~\ref{fig:new-interface}). As seen in Table~\ref{table:participant-summary}, our design changes helped more users connect to Tor in less time. However, many, including users who used the redesigned version, still could not connect to Tor: 63\% (72 of 114) of first attempts failed and 79\% (363 of 458) of total attempts failed. Those that managed to connect took long to do so (>3 minutes in E2 and >20 minutes in E3). Figure~\ref{fig:all-participant-edges} summarizes each participant---showing if they connected to Tor, how long they took to do so, and where they spent their time. Based on these results, we recommend that our changes be adapted in the meantime, but encourage a drastic redesign of the interface.

@@

Table~\ref{tab:attempts-bridge-proxy} shows participants' connections to Tor. As reported in the first two columns, most participants who did not need to configure anything (E1) didn't, although some optionally used a bridge. Participants who could have used any bridge (E2) all used the recommended bridge. Participants who needed a meek bridge or custom bridge (E3) chose a meek bridge at random; the ones who tried to use a custom bridge did not format their messages or inputs correctly and failed to connect to Tor.

@@

Figure~\ref{fig:time_to_success_active_clamped} shows that participants' active configuration time was generally a small fraction of their connection time. The configuration time of participants in E1 was dominated by the time waiting for a connection to be established to Tor because they generally chose the correct configuration right away. The configuration time of participants in E3 was also dominated by the time waiting for a connection to be established to Tor, because they usually needed to try multiple configuration options before connecting, but had to wait for the connection to time out or manually cancel their attempt between attempts. The configuration time of participants in E2 was a modest fraction of their connection time, due to a combination of reasons that affected participants in E1 and E3.

>>>>

\section{Quantitative Testing}
\label{sec:quantitative}
We conducted our quantitative experiments at a behavioral laboratory with many participants in parallel, using instrumentation to capture evaluation metrics. We confirmed prior stumbling points and user behaviors and validated our proposed design improvements.

@@

\subsection{Procedure}
We ran our experiment at Xlab~\cite{xlab}, an experimental social science laboratory. Xlab had 36 workstations with identical Windows~7 laptops, with workstation partitions to discourage participants from looking at others' screens. At the beginning of each session, we used a script to revert the computers to a clean image; download Firefox, Chrome, Internet Explorer, VLC media player, and Tor Browser 5.0.3 (instrumented versions that logged user interactions, with or without our proposed UI changes); set up one of the three simulated environments (E1, E2, or E3); and start recording the computer screen. We manually assigned interface--environment combinations to each computer.

We received informed consent after describing the study (Appendix~\ref{quantitative-script}). We instructed participants to use Tor to complete their worksheet (Appendix~\ref{summative-worksheet}) and gave them 40 minutes to complete the task. Researchers maintained minimal interaction with the participants. After the experiment and exit survey (Appendix~\ref{quantitative-exit-survey}), we gave each participant \$30 for their time.

\subsection{Results} 
In this section, we use OLD to refer to the original interface (Figure~\ref{fig:old-interface}) and NEW to refer the version with our changes (Figure~\ref{fig:new-interface}). As seen in Table~\ref{table:participant-summary}, our design changes helped more users connect to Tor in less time. However, many, including participants who used the redesigned version, still could not connect to Tor: 63\% (72 of 114) of first attempts failed and 79\% (363 of 458) of total attempts failed. Those that managed to connect took long to do so (>3 minutes in E2 and >20 minutes in E3). Figure~\ref{fig:all-participant-edges} summarizes each participant---showing if they connected to Tor, how long they took to do so, and where they spent their time. Based on these results, we recommend that our changes be adapted in the meantime, but encourage a drastic redesign of the interface.

@@

Table~\ref{tab:attempts-bridge-proxy} shows participants' connections to Tor. As reported in the first two columns, most participants who did not need to configure anything (E1) didn't, although some optionally used a bridge. Participants who could have used any bridge (E2) all used the recommended bridge. Participants who needed a \texttt{meek} bridge or custom bridge (E3) chose a \texttt{meek} bridge at random; the ones who tried to use a custom bridge did not format their messages or inputs correctly and failed to connect to Tor.

@@

Figure~\ref{fig:time_to_success_active_clamped} shows that participants' active configuration time was generally a small fraction of their connection time. The configuration time of participants in E1 was dominated by the time waiting for a connection to be established to Tor because they generally chose the correct configuration right away. The configuration time of participants in E3 was also dominated by the time waiting for a connection to be established to Tor, because they usually needed to try multiple configuration options before connecting, but had to wait for the connection to time out or manually cancel their connection between attempts. The configuration time of participants in E2 was a modest fraction of their connection time, due to a combination of reasons that affected participants in E1 and E3.
